Convergence rate of MAP estimates \\ for the exponential family

### 2021-11-02 aistats.tex
Emphasize that SMD converges in the MAP example

As we saw in \S\ref{sec:problem}, MAP can be interpreted as stochastic mirror descent (SMD).
This means that \textbf{1)} we may obtain a convergence rate for MAP from an optimization analysis, and \textbf{2)} any insights gained from the MAP may inform other designs and analyses of SMD.
We first review the assumptions of relative smoothness, helpful to deal with non-smooth functions, before investigating recent analyses of SMD with the MAP.

>>>>

As we saw in \S\ref{sec:problem}, MAP  is a special case of stochastic mirror descent (SMD).
This means that \textbf{1)} we may obtain a convergence rate for MAP from an optimization analysis, and \textbf{2)} any insights gained from MAP may inform other designs and analyses of SMD.
In particular, we know that MAP converges asymptotically as $O(n^{-1})$, so we hope to find a convergence rate for SMD that could capture this behavior. 
We first review the assumptions of relative smoothness, helpful to deal with non-smooth functions, before investigating recent analyses of SMD with the MAP.
